The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-21 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \centering
    \includegraphics{figures/onezone_prompt.pdf}
    \caption{One-zone model abundance tracks and distributions for variants of the prompt DTD.}
    \label{fig:onezone-prompt}
    \script{onezone_prompt.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/ofe_feh_dtd.pdf}
    \caption{Similar to Figure \ref{fig:ofe-feh-sfh} but comparing multi-zone simulations with different DTD models. All assume an inside-out SFH.}
    \label{fig:ofe-feh-dtd}
    \script{ofe-feh-dtd.py}
\end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/onezone_twopopulation.pdf}
    \caption{One-zone model abundance tracks and distributions for variants of the prompt DTD.}
    \label{fig:onezone-prompt}
    \script{onezone_twopopulation.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/ofe_feh_dtd.pdf}
    \caption{Similar to Figure \ref{fig:ofe-feh-sfh} but comparing multi-zone simulations with different DTD models. All assume an inside-out SFH. Each row contains star particles from a different bin in $|z|$, with stars closest to the midplane in the bottom row and stars farthest from the midplane in the top row. All panels present stars within the Solar annulus ($7\leq R_{\rm gal}<9$ kpc).}
    \label{fig:ofe-feh-dtd}
    \script{ofe-feh-dtd.py}
\end{figure*}
